Supplemental Material: Multidimensional analysis and detection of informative features in human white matter

### 2021-01-25 reports/manuscript/abstract.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

\begin{abstract}
    The white matter contains long-range connections between different
    brain regions and the organization of these connections holds important
    implications for brain function in health and disease. Tractometry
    uses diffusion-weighted magnetic resonance imaging (dMRI) data
    to quantify tissue properties (e.g. fractional anisotropy (FA),
    mean diffusivity (MD), etc.), along the trajectories of these
    connections\cite{yeatman2012tract}. Statistical inference from
    tractometry usually either (a) averages these quantities along
    the length of each bundle in each individual, or (b) performs analysis
    point-by-point along each bundle, with group comparisons or regression
    models computed separately for each point along every one of the bundles.
    These approaches are limited in their sensitivity, in the former case, or
    in their statistical power, in the latter.
    In the present work, we developed a method based on the sparse group
    lasso (SGL) \cite{simon2013sparse} that takes into account tissue
    properties measured along all of the bundles, and selects informative
    features by enforcing sparsity, not only at the level of individual
    bundles, but also across the entire set of bundles and all of the measured
    tissue properties. The sparsity penalties for each of these constraints
    is identified using a nested cross-validation scheme that guards
    against over-fitting and simultaneously identifies the correct
    level of sparsity. We demonstrate the accuracy of the method in two
    settings: i) In a classification setting, patients with amyotrophic
    lateral sclerosis (ALS) are accurately distinguished from matched
    controls \cite{sarica2017corticospinal}. Furthermore, SGL automatically
    identifies FA in the corticospinal tract as important for this
    classification -- correctly finding the parts of the white matter known
    to be affected by the disease. ii) In a regression setting, dMRI is
    used to accurately predict ``brain age'' \cite{yeatman2014lifespan,
    Brown2012-so}. In this case, the weights are distributed throughout the
    white matter indicating that many different regions of the white matter
    change with development and contribute to the prediction of age. Thus,
    SGL makes it possible to leverage the multivariate relationship between
    diffusion properties measured along multiple bundles to make accurate
    predictions of subject characteristics while simultaneously discovering
    the most relevant features of the white matter for the characteristic of
    interest.
\end{abstract}

>>>>

\begin{abstract}
    The white matter contains long-range connections between different
    brain regions and the organization of these connections holds important
    implications for brain function in health and disease. Tractometry
    uses diffusion-weighted magnetic resonance imaging (dMRI) data
    to quantify tissue properties (e.g. fractional anisotropy (FA),
    mean diffusivity (MD), etc.), along the trajectories of these
    connections \cite{yeatman2012tract}. Statistical inference from
    tractometry usually either (a) averages these quantities along
    the length of each bundle in each individual, or (b) performs analysis
    point-by-point along each bundle, with group comparisons or regression
    models computed separately for each point along every one of the bundles.
    These approaches are limited in their sensitivity, in the former case, or
    in their statistical power, in the latter.
    In the present work, we developed a method based on the sparse group
    lasso (SGL) \cite{simon2013sparse} that takes into account tissue
    properties measured along all of the bundles, and selects informative
    features by enforcing sparsity, not only at the level of individual
    bundles, but also across the entire set of bundles and all of the measured
    tissue properties.
    % The sparsity penalties for each of these constraints
    % is identified using a nested cross-validation scheme that guards
    % against over-fitting and simultaneously identifies the correct
    % level of sparsity.
    We demonstrate the accuracy of the method in two
    settings: i) In a classification setting, patients with amyotrophic
    lateral sclerosis (ALS) are accurately distinguished from matched
    controls \cite{sarica2017corticospinal}. Furthermore, SGL automatically
    identifies FA in the corticospinal tract as important for this
    classification, correctly finding the parts of the white matter known
    to be affected by the disease. ii) In a regression setting, dMRI is
    used to accurately predict ``brain age'' \cite{yeatman2014lifespan,
    Brown2012-so}. In this case, the weights are distributed throughout the
    white matter indicating that many different regions of the white matter
    change with development and contribute to the prediction of age. Thus,
    SGL makes it possible to leverage the multivariate relationship between
    diffusion properties measured along multiple bundles to make accurate
    predictions of subject characteristics while simultaneously discovering
    the most relevant features of the white matter for the characteristic of
    interest.
\end{abstract}

### 2021-01-25 reports/manuscript/sections/conclusion.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

We present here a novel method for analysis of dMRI tractometry data that relies
on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
predictions of phenotypic properties of individual subjects while,
simultaneously, (b) identifying the features of the white matter that are most
important for this prediction in a completely data-driven approach. The method
is broadly applicable to a wide range of research questions: it performs well in
predicting both continuous variables, such as biological age, as well as
categorical variables, such as whether a person is a patient or a healthy
control. In both of these cases, SGL out-performs previous algorithms that have
been developed for these tasks \cite{sarica2017corticospinal, Richard2018-ux}.
The nested cross-validation approach used to fit the model and make both
predictions and inferences from the model guards against overfitting and tunes
the degree of sparseness required by the algorithm. This means that SGL can
accurately describe phenomena that are locally confined to a particular
anatomical location or diffusion property (e.g., FA in the CST) as well as
phenomena that are widely distributed amongst brain regions and measured
diffusion properties.

Specifically, we demonstrated that the algorithm correctly detects
the fact that ALS, which is a disease of lower motor neurons, is
localized to the cortico-spinal tract. This recapitulates the results
of previous analysis of these same data, using a targeted ROI-based
approach \cite{sarica2017corticospinal}. In contrast, for the analysis
of biological age, the coefficients identified by the algorithm are very
widely distributed across many parts of the white matter, mirroring
previous results with this dataset (and others) that show a large and
continuous distribution of life-span changes in white matter properties
\cite{yeatman2014lifespan}.

@@

Neuroscience has entered an era in which consortium efforts are putting together
large datasets of high-quality dMRI measurements to address a variety of
scientific questions \cite{jernigan2016ping, jernigan2018abcd,
alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
these data pose a substantial challenge. Dimensionality reduction with
tractometry, followed by analysis with the approach we present here promises to
capitalize on the wealth of data and on the co-measurement of interesting and
important phenotypical data about brain health and about the participants'
cognitive abilities. We also expect the group-regularized approach to improve
with larger datasets.

>>>>

We present here a novel method for analysis of dMRI tractometry data that
relies on the Sparse Group Lasso \cite{simon2013sparse} to (a) make accurate
predictions of phenotypic properties of individual subjects while,
simultaneously, (b) identifying the features of the white matter that are
most important for this prediction in a completely data-driven approach. The
method is broadly applicable to a wide range of research questions: it
performs well in predicting both continuous variables, such as biological
age, as well as categorical variables, such as whether a person is a patient
or a healthy control. In both of these cases, SGL out-performs previous
algorithms that have been developed for these tasks
\cite{sarica2017corticospinal, Richard2018-ux, mcpherson2020single}. The
nested cross-validation approach used to fit the model and make both
predictions and inferences from the model guards against overfitting and
tunes the degree of sparseness required by the algorithm. This means that SGL
can accurately describe phenomena that are locally confined to a particular
anatomical location or diffusion property (e.g., FA in the CST) as well as
phenomena that are widely distributed amongst brain regions and measured
diffusion properties.

Specifically, we demonstrated that the algorithm correctly detects the fact
that ALS, which is a disease of lower motor neurons, is localized to the
cortico-spinal tract. This recapitulates the results of previous analysis of
these same data, using a targeted ROI-based approach
\cite{sarica2017corticospinal}. In contrast, for the analysis of biological
age, the coefficients identified by the algorithm are very widely distributed
across many parts of the white matter, mirroring previous results that show a
large and continuous distribution of life-span changes in white matter
properties \cite{yeatman2014lifespan}.

@@

Neuroscience has entered an era in which consortium efforts are amassing
large datasets of high-quality dMRI measurements to address a variety of
scientific questions \cite{jernigan2016ping, jernigan2018abcd,
alexander2017open, Miller2016-hw, VanEssen2012}. The volume and complexity of
these data pose a substantial challenge. Dimensionality reduction with
tractometry, followed by analysis with the approach we present here promises to
capitalize on the wealth of data and on the co-measurement of interesting and
important phenotypical data about brain health and about the participants'
cognitive abilities. We also expect the group-regularized approach to improve
with larger datasets.

### 2021-01-25 reports/manuscript/sections/introduction.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

\section*{Introduction}

@@

Leveraging this fact, one of the most powerful methods currently
available to put macro- and micro-structure together is
\emph{tractometry}: assessment of the physical properties of the white
matter along specific tracts \cite{Bells2011-cf}. Though there are
several different available implementations of this overall idea,
the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
the parts of the white matter that belong to different major ``tracts''
(i.e. anatomical or functional groups of white matter fibers), such as
the corticospinal tract or arcuate fasciculus, assigning tractography
generated streamlines to ``bundles,'' which approximate the anatomical
tracts, and sampling biophysical properties (such as fractional
anisotropy or mean diffusivity) along the length of these bundles.
the parts of the white matter that belong to different major tracts
(i.e. anatomical or functional groups of white matter fibers), such as
the corticospinal tract or arcuate fasciculus, assigning tractography
generated streamlines to ``bundles,'' which approximate the anatomical
tracts, and sampling biophysical properties (such as fractional
anisotropy or mean diffusivity) along the length of these bundles. In
some previous tractometry-based studies, tissue properties along the
length of each tract were summarized by taking the mean along each
bundle, but there is a large body of evidence showing that there is
systematic variability in the values of diffusion metrics along the
trajectory of each bundle. This justifies retaining the individual
samples along the length of each bundle \cite{yeatman2012tract,
colby2012, ODonnell2009-uu}. While this retains important information
about each individual's white matter, it also presents statistical
challenges due to the dimensionality of the data. Based on tractometry,
researchers may choose to compare different individuals to each other.
This is usually done according to one of the following approaches:

>>>>

\subsection*{Introduction}

\begin{figure}[!h]
    \vspace{0.25cm}
    \rlap{
        \hspace{0.5em}
        \includegraphics[width=0.98\columnwidth]{methods-brains.pdf}
    }
    \vspace{-9.75cm}
    \includegraphics[width=\columnwidth]{method-quad.pdf}
    {\phantomsubcaption\label{fig:methods:tractogram}}
    {\phantomsubcaption\label{fig:methods:cst}}
    {\phantomsubcaption\label{fig:methods:tract-profile}}
    {\phantomsubcaption\label{fig:methods:group-structure}}
    \caption{{\bf Tractometry data lineage}
        \label{fig:methods}
        {\bf (a)} Whole brain tractography generates streamlines approximating
        the trajectories of white matter connections.
        {\bf (b)} Tractometry classifies these streamlines into anatomical bundles.
        In this case, we show the left corticospinal tract (CSTL) over a mid-saggital
        anatomical slice.
        {\bf (c)} Tractometry further extracts bundle profiles,
        quantifications of various diffusion metrics along the length of the
        fiber bundle. Here, we show one subject's fractional anisotropy (FA)
        profile for CSTL.
        {\bf (d)} the phenotypical target data and tractometric features can
        be organized into a linear model, $\hat{y} = \mathbf{X}
        \hat{\beta}$. The feature matrix $\mathbf{X}$ is color-coded
        to reveal a natural group structure: the left (orange) group
        contains $k$ features from the CSTL, the middle (green) group
        contains $k$ features from the left cingulum cingulate (CGCL),
        and the right (blue) group
        contains $k$ features from the left arcuate (ARCL). The coefficients in
        $\hat{\beta}$ follow the same natural grouping.
        % Cross-validation:
        % we evaluate model quality using a nested $k$-fold cross validation
        % scheme. At level-0, the input data is decomposed into $k$
        % shuffled groups and optimal hyperparameters are found for the level-0
        % training set.
        % To avoid overfitting, the optimal hyperparameters are themselves
        % evaluated using a cross-validation scheme taking place
        % at level-1 of the decomposition, where each
        % level-0 training set is further decomposed into five shuffled
        % groups. For the ALS and WH data, $k=10$, while for the HBN and
        % Cam-CAN data, $k=5$.
    }
\end{figure}

\todo[inline]{The introduction section should be shortened for Nature methods
I think.}

@@

Leveraging this fact, one of the most powerful methods currently
available to put macro- and micro-structure together is
\emph{tractometry}: assessment of the physical properties of the white
matter along specific tracts \cite{Bells2011-cf}. Though there are
several different available implementations of this overall idea,
the principles are similar \cite{yeatman2012tract, Yendiki2011-ay,
Wassermann2016-iv, ODonnell2009-uu}: tractometry begins by delineating
the parts of the white matter that belong to different major ``tracts''
(i.e. anatomical or functional groups of white matter fibers), such as
the corticospinal tract or arcuate fasciculus, assigning tractography
generated streamlines to ``bundles,'' which approximate the anatomical
tracts, and sampling biophysical properties, such as fractional
anisotropy (FA) or mean diffusivity (MD), along the length of these bundles.
the parts of the white matter that belong to different major tracts
(i.e. anatomical or functional groups of white matter fibers), such as
the corticospinal tract or arcuate fasciculus, assigning tractography
generated streamlines to ``bundles,'' which approximate the anatomical
tracts, and sampling biophysical properties (such as fractional
anisotropy or mean diffusivity) along the length of these bundles. In
some previous tractometry-based studies, tissue properties along the
length of each tract were summarized by taking the mean along each
bundle, but there is a large body of evidence showing that there is
systematic variability in the values of diffusion metrics along the
trajectory of each bundle. This justifies retaining the individual
samples along the length of each bundle \cite{yeatman2012tract,
colby2012, ODonnell2009-uu}. While this retains important information
about each individual's white matter, it also presents statistical
challenges due to the dimensionality of the data. Based on tractometry,
researchers may choose to compare different individuals to each other.
This is usually done according to one of the following approaches:

### 2021-01-25 reports/manuscript/sections/results.tex
Add nested cross-val figure. Update figures and text to remove underscores in bundle names. Add text to describe bundle profiles in supplementary material.

\begin{figure*}
    \vspace{3cm}
    \rlap{
        \includegraphics[width=0.33\textwidth]{als_coefs.pdf}
    }
    \vspace{-8.4cm}
    \includegraphics[width=\textwidth]{als_results.pdf}
    {\phantomsubcaption\label{fig:class-results:probs}}
    {\phantomsubcaption\label{fig:class-results:coefs3d}}
    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
    {\phantomsubcaption\label{fig:class-results:false-positives}}
    {\phantomsubcaption\label{fig:class-results:false-negatives}}
    \caption{%
        {\bf SGL accurately and interpretably predicts ALS diagnosis.}
        \label{fig:class-results}
        {\bf (a)} Classification probabilities for ALS diagnosis, with
        controls on the left, patients on the right, predicted controls in
        blue, and predicted patients in orange. So orange dots on the left
        represent false positives, while blue dots on the right represent
        false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
        ROC AUC of {\protect\alsRocAuc}.
        {\bf (b)} SGL coefficients are presented on the core fibers of major
        fiber bundles. They exhibit high group sparsity and are concentrated
        in the fa of the CST. The brain is oriented with the right hemisphere
        in the foreground and anterior to the right of the page. The CST\_L,
        CST\_R, and CF\_A bundles are indicated for orientation.
        {\bf (c)} SGL identifies three portions of the CST as important,
        where $\hat{\beta}$ (dashed line, right axis) has large values. These
        are centered around nodes 30, 65, and 90, corresponding to locations
        of substantial differences in FA between the ALS and control groups
        (shaded areas indicates standard error of the mean).
        {\bf (d)} Bundle profiles for false positive classifications. Line
        colors correspond to the marker edge color in the top left plot.
        These individuals have reduced FA in the CST portions which SGL
        identified as important. Their misclassification is coherent with the
        feature importance and the group differences in FA.
        {\bf (e)} Individual bundle profiles for false negative
        classifications. These individuals have bundle profiles which
        oscillate between the group means.
    }
\end{figure*}

@@

Using data from a previous study of the corticospinal tract (CST) profile and
ALS \cite{sarica2017corticospinal}, we tested the performance of SGL in a
classification setting. The previous study predicted ALS status with a mean
accuracy of 80\% using a random forest algorithm based on a priori selection
of features within the corticospinal tract. SGL delivers competitive
predictive performance (mean {\alsAccuracy}\% accuracy, {\alsRocAuc} ROC AUC)
without the need for a priori feature engineering. The results of the
classification prediction are shown in \cref{fig:class-results:probs} with
``ground-truth'' ALS status separated into columns, and predicted ALS status
encoded by color. In addition to this classification performance, SGL also
identifies the white matter tracts most important for ALS classification. The
relative importance of white matter features is captured in the $\beta$
coefficients from \cref{supp:eq:sgl}. \Cref{fig:class-results:tract-profiles}
depicts these coefficients along the right CST, plotted over the FA values
for the control and ALS subject groups. We find that SGL selects FA metrics
in the corticospinal tract and particularly in the right corticospinal tract
as most important to ALS classification, confirming previous findings
\cite{van2011upper, toosy2003diffusion, sarica2014tractography,
sage2007quantitative, sage2009quantitative, karlsborg2004corticospinal,
ellis1999diffusion, cosottini2005diffusion, ciccarelli2009investigation,
abe2010voxel} and identifying the portions of the brain that were selected
\emph{a priori} in the previous study from which we collected our data
\cite{sarica2017corticospinal}.

The $\beta$ coefficients exhibit high bundle level sparsity; only some
bundles are important, which can be be confirmed by observing the value of
$\alpha$ in \cref{supp:eq:sgl}, the regularization hyperparameter that
controls the mixture of the group lasso and lasso penalties. If $\alpha$ is
closer to zero, it indicates that the phenotype in question preferentially
correlates with only a few groups of covariates. For the ALS dataset, $\alpha
= $ \alsLRatio, confirming that the white matter correlates of ALS reside
mostly in one bundle, namely the CST.

@@

To test the performance of SGL with tractometry data in a continuous
regression task, we focus here on the prediction of biological age based on
tractometry data in three datasets named WH, HBN, and Cam-CAN (see
\cref{supp:sec:data} for further details). Prediction of ``brain age'' is a
commonly undertaken task in neuroimaging machine learning, in part because
these predictions, and deviations therefrom, may be diagnostic of overall
brain health (for a review, see \textcite{Cole2019-rz}). However, as
\textcite{nelson2019biomarkers} have observed, aging biomarkers are subject
to unique challenges and tend to be noncausative. Our interest in aging here
relies on its utility as a methodological benthmark. Biological age operates
on a natural scale, with meaningful and easily understood units, and it's
popularity as a machine learning target makes it valuable for comparisons
with other studies.

The WH \cite{yeatman2014lifespan}, HBN \cite{alexander2017open}, and Cam-CAN
\cite{shafto2014cambridge,taylor2017cambridge} datasets used here contain
data from 76, 978, and 640 subjects, respectively, ranging from 6-50, 5-21,
and 18-88 years of age, respectively. In each case, biological age was used
as the predicted variable ($y$ in \cref{supp:eq:lm}). SGL was fit to
tractometry-extracted features in 18 major brain tracts: DTI FA and DTI MD
for WH and DKI FA and DKI MD for HBN and Cam-CAN, with each tract divided
into 100 nodes.

To evaluate the fit of the model, we used a nested cross-validation
procedure. In this procedure, batches of subjects are held out. For each
batch (or fold), the model is fully fit without this data. Then, once the
parameters are fixed, the model is inverted to predict the ages of held out
subjects based on the linear coeffiecients. This scheme automatically finds
the right level of regularization (i.e., sparseness) and fits the
coefficients to the ill-posed linear model, while guarding against
overfitting. SGL accurately predicts the age of the subjects in this
procedure, with a median absolute error of 2.8 years, 1.5 years, and 6.0
years for WH, HBN, and Cam-CAN, respectively and coefficients of
determination $R^2 = $ {\whRsq} , {\hbnRsq}, and {\camcanRsq}, respectively (see
\cref{fig:age-results}, top panels). The predictions for Cam-CAN are
competitive with a recent state of the art prediction
\cite{mcpherson2020single}, which used streamline density to estimate the
brain's structural connectivity and achieved $R^2 = 0.63$. The median
absolute errors are also lower than the results of a recent study that
predicted age in a large sample, based on diffusion MRI features
\cite{Richard2018-ux}.

>>>>

\begin{figure*}
    \vspace{3cm}
    \rlap{
        \includegraphics[width=0.33\textwidth]{als_coefs.pdf}
    }
    \vspace{-8.4cm}
    \includegraphics[width=\textwidth]{als_results.pdf}
    {\phantomsubcaption\label{fig:class-results:probs}}
    {\phantomsubcaption\label{fig:class-results:coefs3d}}
    {\phantomsubcaption\label{fig:class-results:tract-profiles}}
    {\phantomsubcaption\label{fig:class-results:false-positives}}
    {\phantomsubcaption\label{fig:class-results:false-negatives}}
    \caption{%
        {\bf SGL accurately and interpretably predicts ALS diagnosis.}
        \label{fig:class-results}
        {\bf (a)} Classification probabilities for ALS diagnosis, with
        controls on the left, patients on the right, predicted controls in
        blue, and predicted patients in orange. So orange dots on the left
        represent false positives, while blue dots on the right represent
        false negatives. We achieve {\protect\alsAccuracy}\% accuracy with an
        ROC AUC of {\protect\alsRocAuc}.
        {\bf (b)} SGL coefficients are presented on the core fibers of major
        fiber bundles. They exhibit high group sparsity and are concentrated
        in the FA of the CST. The brain is oriented with the right hemisphere
        in the foreground and anterior to the right of the page. The CSTL,
        CSTR, and CFA bundles are indicated for orientation.
        {\bf (c)} SGL identifies three portions of the CST as important,
        where $\hat{\beta}$ (dashed line, right axis) has large values. These
        are centered around nodes 30, 65, and 90, corresponding to locations
        of substantial differences in FA between the ALS and control groups
        (shaded areas indicates standard error of the mean).
        {\bf (d)} Bundle profiles for false positive classifications. Line
        colors correspond to the marker edge color in the top left plot.
        These individuals have reduced FA in the CST portions which SGL
        identified as important. Their misclassification is coherent with the
        feature importance and the group differences in FA.
        {\bf (e)} Individual bundle profiles for false negative
        classifications. These individuals have bundle profiles which
        oscillate between the group means.
    }
\end{figure*}

@@

Using data from a previous study of the corticospinal tract (CST) profile and
ALS \cite{sarica2017corticospinal}, we tested the performance of SGL in a
classification setting. The previous study predicted ALS status with a mean
accuracy of 80\% using a random forest algorithm based on a priori selection
of features within the CST. SGL delivers competitive
predictive performance, with a cross-validated accuracy of {\alsAccuracy}\%
and an area under the receiver operating characteristic curve (ROC AUC) of
{\alsRocAuc}, all without the need for a priori feature engineering. The
results of the classification prediction are shown in
\cref{fig:class-results:probs} with ``ground-truth'' ALS status separated
into columns, and predicted ALS status encoded by color. In addition to this
classification performance, SGL also identifies the white matter tracts most
important for ALS classification. The relative importance of white matter
features is captured in the $\beta$ coefficients from \cref{supp:eq:sgl} of
the supplemental material \cite{supplement}.
\Cref{fig:class-results:tract-profiles} depicts these coefficients along the
right CST, plotted over the FA values for the control and ALS subject groups.
We find that SGL selects FA metrics in the corticospinal tract and
particularly in the right corticospinal tract as most important to ALS
classification, confirming previous findings \cite{van2011upper,
toosy2003diffusion, sarica2014tractography, sage2007quantitative,
sage2009quantitative, karlsborg2004corticospinal, ellis1999diffusion,
cosottini2005diffusion, ciccarelli2009investigation, abe2010voxel} and
identifying the portions of the brain that were selected \emph{a priori} in
the previous study from which we collected our data
\cite{sarica2017corticospinal}.

The $\beta$ coefficients exhibit high bundle level sparsity; only some
bundles are important, which can be be confirmed by observing the value of
$\alpha$, the regularization hyperparameter that controls the mixture of the
group lasso and lasso penalties
(see \cref{supp:eq:sgl} of the supplemental material \cite{supplement}).
If $\alpha$ is closer to zero, it indicates that the phenotype in question
preferentially correlates with only a few groups of covariates. For the ALS
dataset, $\alpha = $ \alsLRatio, confirming that the white matter correlates
of ALS reside mostly in one bundle, namely the CST.

@@

To test the performance of SGL with tractometry data in a continuous
regression task, we focus here on the prediction of biological age in three
datasets named WH, HBN, and Cam-CAN (see supplemental material
\cite{supplement} for a description of each dataset). Prediction of ``brain
age'' is a commonly undertaken task in neuroimaging machine learning, in part
because these predictions, and deviations therefrom, may be diagnostic of
overall brain health (for a review, see Cole et al.~\cite{Cole2019-rz}).
However, as Nelson et al.~\cite{nelson2019biomarkers} have observed, aging
biomarkers are subject to unique challenges and tend to be noncausative. Our
interest in aging here relies on its utility as a methodological benthmark.
Biological age operates on a natural scale, with meaningful and easily
understood units, and it's popularity as a machine learning target makes it
valuable for comparisons with other studies.

The WH \cite{yeatman2014lifespan}, HBN \cite{alexander2017open}, and Cam-CAN
\cite{shafto2014cambridge,taylor2017cambridge} datasets used here contain
data from 76, 978, and 640 subjects, respectively, ranging from 6-50, 5-21,
and 18-88 years of age, respectively. In each case, biological age was used
as the predicted variable $y$. SGL was fit to the tractometry-extracted
features FA and MD in 18 major brain tracts, with diffusion metrics extracted
from diffusion tensor imaging (DTI) for the WH dataset and diffusion kurtosis
imaging (DKI) \cite{jensen2005diffusion} the HBN and Cam-CAN datasets.

To evaluate the fit of the model, we used a nested cross-validation
procedure. In this procedure, batches of subjects are held out. For each
batch (or fold), the model is fully fit without this data. Then, once the
parameters are fixed, the model is inverted to predict the ages of held out
subjects based on the linear coeffiecients. This scheme automatically finds
the right level of sparsity and fits the coefficients to the ill-posed linear
model, while guarding against overfitting. SGL accurately predicts the age of
the subjects in this procedure, with a median absolute error of {\whMae},
{\hbnMae}, and {\camcanMae} years for the WH, HBN, and Cam-CAN datasets,
respectively and coefficients of determination $R^2 = $ {\whRsq} , {\hbnRsq},
and {\camcanRsq}, respectively (see \cref{fig:age-results}, top panels). The
predictions for Cam-CAN are competitive with a recent state of the art
prediction \cite{mcpherson2020single}, which used streamline density to
estimate the brain's structural connectivity and achieved $R^2 = 0.63$. The
median absolute errors are also lower than the results of a recent study that
predicted age in a large sample, based on diffusion MRI features
\cite{Richard2018-ux}.
